Your Title Here

### 2025-05-15 latex/draft.tex
更新论文

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[style=authoryear, backend=biber]{biblatex} % 使用biblatex
\addbibresource{references.bib} % 确保你的.bib文件名称正确
\usepackage{graphicx}
\usepackage{booktabs} % 专业表格宏包
\usepackage{array}    % 增强表格对齐
\usepackage{tabularx} % 可选：适应文本宽度
\usepackage{placeins} % 在导言区添加
\usepackage{ragged2e}  % 文本对齐优化

@@

@@

\subsection{Sources}
The distribution of publications and citation impact across journals reveals distinct patterns in drone logistics research. Drones leads in publication volume (98 papers) but has the lowest average citations (7.34) among top-output journals. Subsequent examination of highly cited articles in Drones suggests a focus on rapid dissemination of applied or technical studies (\cite{WOS:000682822500001, WOS:000682822500021}). SUSTAINABILITY (57 papers, 16.88 avg. citations) ranks second in publication volume, reflecting its role in hosting interdisciplinary studies on drone logistics' environmental and societal impacts (\cite{WOS:000531558100214, WOS:000428567100315}). IEEE TRANSACTIONS ON INTELLIGENT TRANSPORTATION SYSTEMS (57 papers, 28.40 avg. citations) matches SUSTAINABILITY in output but achieves higher citations, indicative of its focus on routing innovations (\cite{WOS:000658360600026}) and UAV integration into adaptive traffic systems (\cite{WOS:000684003100038}). TRANSPORTATION RESEARCH PART C-EMERGING TECHNOLOGIES (53 papers) achieves the highest average citations (79.15) in this category, reflecting its prominence in publishing high-impact applied optimization studies (\cite{WOS:000353871700006, WOS:000425566000035}). IEEE ACCESS (46 papers, 16.00 avg. citations) and APPLIED SCIENCES-BASEL (38 papers, 7.50 avg. citations) prioritize rapid dissemination of applied research, with IEEE ACCESS showing marginally higher citation influence due to its engineering-focused scope. TRANSPORTATION RESEARCH PART E-LOGISTICS AND TRANSPORTATION REVIEW (36 papers, 34.31 avg. citations) publishes strategic analyses of drone logistics' cost-efficiency and supply chain integration (\cite{WOS:000488423300001}). EUROPEAN JOURNAL OF OPERATIONAL RESEARCH (33 papers, 29.73 avg. citations) and COMPUTERS \& INDUSTRIAL ENGINEERING (31 papers, 29.55 avg. citations) demonstrate balanced output and citations, focusing on operational research (\cite{WOS:000742554100008}) and computational methods for UAV routing (\cite{WOS:000460496000002}). Drone logistics research exhibits a dichotomy between high-output, application-focused journals (e.g., Drones with 98 papers) and lower-output, high-impact journals (e.g., Transportation Research Part C with 79.15 avg. citations).

@@

>>>>

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[style=authoryear, backend=biber]{biblatex} % 使用biblatex
\addbibresource{references.bib} % 确保你的.bib文件名称正确
\usepackage{graphicx}
\usepackage{booktabs} % 专业表格宏包
\usepackage{array}    % 增强表格对齐
\usepackage{tabularx} % 可选：适应文本宽度
\usepackage{placeins} % 在导言区添加
\usepackage{ragged2e}  % 文本对齐优化
\usepackage{float}

@@

\usepackage{subcaption}  % 关键宏包必须加载
\usepackage{geometry}
\geometry{a4paper, margin=1.5cm}

% 正确定义子表格模板
\newcommand{\metricstable}[3]{%
  \begin{minipage}{0.32\textwidth}
  \centering
  \begin{tabularx}{\linewidth}{@{} >{\raggedright\arraybackslash}X r @{}}
    \toprule
    \textbf{Institution} & \textbf{#2} \\
    \midrule
    #3
    \bottomrule
  \end{tabularx}
  \end{minipage}
}

@@

\begin{table}[htbp]
  \centering
  \caption{Top 10 Institutions by Total Citations}
  \label{tab:citations}
  \begin{tabularx}{0.9\textwidth}{@{} >{\raggedright}X r @{}}
    \toprule
    Institution & Total Citations \\
    \midrule
    Sejong University & 1712 \\
    Auburn University & 1062 \\
    Purdue University & 1041 \\
    University System of Maryland & 947 \\
    University of Maryland & 883 \\
    York University - Canada & 863 \\
    State University System of Florida & 821 \\
    University of Calgary & 807 \\
    State University of New York (SUNY) System & 798 \\
    Erasmus University Rotterdam & 763 \\
    \bottomrule
  \end{tabularx}
\end{table}

%% 表2：论文数量排名
\begin{table}[htbp]
  \centering
  \caption{Top 10 Institutions by Publications} 
  \label{tab:publications}
  \begin{tabularx}{0.9\textwidth}{@{} >{\raggedright}X r @{}}
    \toprule
    Institution & Publications \\
    \midrule
    Hong Kong Polytechnic University & 42 \\
    Nanjing University of Aeronautics \& Astronautics & 33 \\
    Beihang University & 28 \\
    Sejong University & 27 \\
    National University of Defense Technology - China & 26 \\
    Nanyang Technological University & 22 \\
    Chinese Academy of Sciences & 21 \\
    Tsinghua University & 20 \\
    Purdue University & 19 \\
    University System of Maryland & 19 \\
    \bottomrule
  \end{tabularx}
\end{table}

%% 表3：H指数排名 
\begin{table}[htbp]
  \centering
  \caption{Top 10 Institutions by H-index}
  \label{tab:hindex}
  \begin{tabularx}{0.9\textwidth}{@{} >{\raggedright}X r @{}}
    \toprule
    Institution & H-index \\
    \midrule
    Sejong University & 19 \\
    Hong Kong Polytechnic University & 14 \\
    University of New South Wales Sydney & 13 \\
    Nanyang Technological University & 13 \\
    National University of Defense Technology - China & 12 \\
    Kyung Hee University & 11 \\
    Northwestern Polytechnical University & 11 \\
    Purdue University & 10 \\
    University System of Maryland & 10 \\
    University of Missouri System & 10 \\
    \bottomrule
  \end{tabularx}
\end{table}

\subsection{Sources}
The distribution of publications and citation impact across journals reveals distinct patterns in drone logistics research. Drones leads in publication volume (98 papers) but has the lowest average citations (7.34) among top-output journals. Subsequent examination of highly cited articles in Drones suggests a focus on rapid dissemination of applied or technical studies (\cite{WOS:000682822500001, WOS:000682822500021}). Sustainability (57 papers, 16.88 avg. citations) ranks second in publication volume, reflecting its role in hosting interdisciplinary studies on drone logistics' environmental and societal impacts (\cite{WOS:000531558100214, WOS:000428567100315}). IEEE Transactions on Intelligent Transportation Systems (57 papers, 28.40 avg. citations) matches Sustainability in output but achieves higher citations, indicative of its focus on routing innovations (\cite{WOS:000658360600026}) and UAV integration into adaptive traffic systems (\cite{WOS:000684003100038}). Transportation Research Part C: Emerging Technologies (53 papers) achieves the highest average citations (79.15) in this category, reflecting its prominence in publishing high-impact applied optimization studies (\cite{WOS:000353871700006, WOS:000425566000035}). IEEE Access (46 papers, 16.00 avg. citations) and Applied Sciences-Basel (38 papers, 7.50 avg. citations) prioritize rapid dissemination of applied research, with IEEE Access showing marginally higher citation influence due to its engineering-focused scope. Transportation Research Part E: Logistics and Transportation Review (36 papers, 34.31 avg. citations) publishes strategic analyses of drone logistics' cost-efficiency and supply chain integration (\cite{WOS:000488423300001}). European Journal of Operational Research (33 papers, 29.73 avg. citations) and Computers \& Industrial Engineering (31 papers, 29.55 avg. citations) demonstrate balanced output and citations, focusing on operational research (\cite{WOS:000742554100008}) and computational methods for UAV routing (\cite{WOS:000460496000002}). Drone logistics research exhibits a dichotomy between high-output, application-focused journals (e.g., Drones with 98 papers) and lower-output, high-impact journals (e.g., Transportation Research Part C with 79.15 avg. citations).

\begin{table}[htbp]
  \centering
  \caption{Top Journals in Drone Logistics Research (2018-2023)}
  \label{tab:journals}
  \begin{tabularx}{0.9\textwidth}{@{} >{\raggedright}X r r r @{}}
    \toprule
    \textbf{Journal} & \textbf{Pubs.} & \textbf{Total Cites} & \textbf{Cites/Paper} \\
    \midrule
    Drones & 98 & 719 & 7.34 \\
    Sustainability & 57 & 962 & 16.88 \\
    IEEE Transactions on Intelligent Transportation Systems & 57 & 1619 & 28.40 \\
    Transportation Research Part C: Emerging Technologies & 53 & 4195 & 79.15 \\
    IEEE Access & 46 & 736 & 16.00 \\
    Applied Sciences-Basel & 38 & 285 & 7.50 \\
    Transportation Research Part E: Logistics and Transportation Review & 36 & 1235 & 34.31 \\
    European Journal of Operational Research & 33 & 981 & 29.73 \\
    Computers \& Industrial Engineering & 31 & 916 & 29.55 \\
    Sensors & 30 & 533 & 17.77 \\
    \bottomrule
  \end{tabularx}

  \vspace{0.5em}
  \raggedright\footnotesize
\end{table}

\FloatBarrier

@@

\begin{table}[H]
  \centering
  \caption{Evolution of High-Frequency Disciplines in Drone Logistics Research}
  \label{tab:discipline_evolution}

  \begin{minipage}[t]{0.48\textwidth}
  \centering
  \begin{tabularx}{\linewidth}{@{} >{\raggedright}X r @{}}
    \toprule
    \multicolumn{2}{c}{\textbf{Pre-2021 (2000-2020)}} \\
    \midrule
    \textbf{Discipline} & \textbf{Frequency} \\
    \midrule
    Engineering, Electrical \& Electronic & 63 \\
    Operations Research \& Management Science & 56 \\
    Transportation Science \& Technology & 51 \\
    Telecommunications & 44 \\
    Computer Science, Information Systems & 40 \\
    Transportation & 36 \\
    Robotics & 27 \\
    Computer Science, Artificial Intelligence & 26 \\
    Computer Science, Interdisciplinary Applications & 17 \\
    Engineering, Civil & 17 \\
    \bottomrule
  \end{tabularx}
  \end{minipage}
  \hfill
  \begin{minipage}[t]{0.48\textwidth}
  \centering
  \begin{tabularx}{\linewidth}{@{} >{\raggedright}X r @{}}
    \toprule
    \multicolumn{2}{c}{\textbf{Post-2021 (2021-2023)}} \\
    \midrule
    \textbf{Discipline} & \textbf{Frequency} \\
    \midrule
    Engineering, Electrical \& Electronic & 299 \\
    Transportation Science \& Technology & 265 \\
    Operations Research \& Management Science & 255 \\
    Telecommunications & 164 \\
    Computer Science, Information Systems & 150 \\
    Transportation & 142 \\
    Management & 127 \\
    Engineering, Civil & 126 \\
    Computer Science, Artificial Intelligence & 108 \\
    Remote Sensing & 103 \\
    \bottomrule
  \end{tabularx}
  \end{minipage}

  \vspace{0.5em}
  \raggedright\footnotesize
\end{table}

\FloatBarrier
